Presentation Title

### 2017-07-29 presentation/presentation.tex
Edit ch1 and ch2

\begin{frame}{\subsecname}
  \begin{figure}[h]
  \includegraphics[width=0.67\textwidth]{trustchain-good-cp}
  \centering
  \caption{TX block is a six-tuple: $t_{u, i} = \langle \textsf{H}(b_{u, i - 1}), i, txid, pk_v, m, sig_u \rangle$.
    CP block is a five-tuple: $c_{u, i} = \langle \textsf{H}(b_{u, i-1}), i, \textsf{H}(\C_r), r, sig_u \rangle$.}
  \end{figure}
  \note{
    \begin{itemize}
      \item In this example there are three nodes
      \item Squares are TX blocks and circles are CP blocks
      \item Explain the block content in caption
      \item The dotted line represent pairs of TX blocks
      \item Geared with the understanding of our data structure, we are ready to talk about the consensus protocol
    \end{itemize}
  }
\end{frame}

@@

\begin{frame}{\subsecname}
  \begin{figure}[h]
  \includegraphics[width=0.67\textwidth]{trustchain-1}
  \centering
  \caption{Suppose we are in a state where $\C_{r - 1}$ has just been agreed by some facilitators but not yet propagated.}
  \end{figure}
\end{frame}

\begin{frame}{\subsecname}
  \begin{figure}[h]
  \includegraphics[width=0.67\textwidth]{trustchain-2}
  \centering
  \caption{Nodes receive consensus result $\C_{r - 1}$,
    first $n$ nodes ordered by $\textsf{H}(\C_{r-1} || pk)$ become $\F_{r-1}$,
    send the new CP blocks to $\F_{r-1}$.}
  \end{figure}
\end{frame}

\begin{frame}{\subsecname}
  \begin{figure}[h]
  \includegraphics[width=0.67\textwidth]{trustchain-3}
  \centering
  \caption{Transactions carry on as usual in round $r$,
  while facilitators are trying to reach consensus on the new CP blocks concurrently.}
  \end{figure}
\end{frame}

\begin{frame}{\subsecname}
  \begin{figure}[h]
  \includegraphics[width=0.67\textwidth]{trustchain-4}
  \centering
  \caption{$\F_{r-1}$ agree and disseminate $\C_r$,
  CP blocks at round $r-1$ ($c_{a, 6}, c_{b, 4}, c_{c,8}$) should be in $\C_r$.}
  \end{figure}
\end{frame}

>>>>

\begin{frame}{\subsecname}
  \begin{figure}[h]
  \includegraphics[width=0.67\textwidth]{trustchain-good-cp}
  \centering
  \caption*{TX block is a six-tuple: $t_{u, i} = \langle \textsf{H}(b_{u, i - 1}), i, txid, pk_v, m, sig_u \rangle$\\
    CP block is a five-tuple: $c_{u, i} = \langle \textsf{H}(b_{u, i-1}), i, \textsf{H}(\C_r), r, sig_u \rangle$}
  \end{figure}
  \note{
    \begin{itemize}
      \item In this example there are three nodes
      \item Squares are TX blocks and circles are CP blocks
      \item Explain the block content in caption
      \item The dotted line represent pairs of TX blocks
      \item Geared with the understanding of our data structure, we are ready to talk about the consensus protocol
    \end{itemize}
  }
\end{frame}

@@

\begin{frame}{\subsecname}
  \begin{figure}[h]
  \includegraphics[width=0.67\textwidth]{trustchain-1}
  \centering
  \caption*{Suppose we are in a state where $\C_{r - 1}$ has just been agreed by some facilitators but not yet propagated.}
  \end{figure}
\end{frame}

\begin{frame}{\subsecname}
  \begin{figure}[h]
  \includegraphics[width=0.67\textwidth]{trustchain-2}
  \centering
  \caption*{Nodes receive consensus result $\C_{r - 1}$,
    first $n$ nodes ordered by $\textsf{H}(\C_{r-1} || pk)$ become $\F_{r-1}$,
    send the new CP blocks to $\F_{r-1}$.}
  \end{figure}
\end{frame}

\begin{frame}{\subsecname}
  \begin{figure}[h]
  \includegraphics[width=0.67\textwidth]{trustchain-3}
  \centering
  \caption*{Transactions carry on as usual in round $r$,
  while facilitators are trying to reach consensus on the new CP blocks concurrently.}
  \end{figure}
\end{frame}

\begin{frame}{\subsecname}
  \begin{figure}[h]
  \includegraphics[width=0.67\textwidth]{trustchain-4}
  \centering
  \caption*{$\F_{r-1}$ agree and disseminate $\C_r$,
  CP blocks at round $r-1$ ($c_{a, 6}, c_{b, 4}, c_{c,8}$) should be in $\C_r$.}
  \end{figure}
\end{frame}

### 2017-07-29 thesis/chapters/ch1-intro.tex
Write more design variations
Edit ch1 and ch2

We live in a world where technologies have become vital for our welfare and success.
The internet, for instance, gave us the ability of efficiently exchange information on a global scale.
However, in contrast to its original design, the internet and in particular the world wide web is becoming increasingly centralised.
The domain name system (root name server), certificate authorities (root CA), to name a few, carry enormous responsibilities and are a central point of failure.
The  same can be said for many other services such are online marketplaces,
cloud services, hospitality services and even our banking system.
The 2008 financial crisis is an example of the banking system making poor choices which result in a
decline in consumer wealth in the order of trillions~\cite{financialcrisis} and led to the European debt crisis.

Ironically, also in 2008, Satoshi Nakamoto published the Bitcoin whitepaper~\cite{bitcoin}.
Which, for the first time, gave us a simple banking system in the form of a distributed ledger.
It needs no central control but still incorruptable with high probability even if there are malicious parties that aim to undermine the system.
We call such a ledger a blockchain.

The primary innovations are (1) its consensus model which prevents double spending,
and (2) its incentive mechanism that encourages anyone (with adaquate hardware) to participate in the network and keep it running.
The double spending problem can be seen as an inconsistency issue.
For example, $C$ has 5 units of currency in her account.
At some instant in time, $A$ sees that $C$ transferred 5 units to $A$ and $B$ sees that $C$ transferred 5 units to $B$.
Hence the transaction is inconsistent with respect to the observer.
Bitcoin and many of its derivatives (e.g. Litecoin\footnote{\url{litecoin.org}} and Dogecoin\footnote{\url{dogecoin.org}}) solve the inconsistency problem with a consensus algorithm.
The goal of the algorithm is reach agreement on a set of valid values, e.g. transactions. 
This effectively eliminates inconsistencies.
In Bitcoin's case, the consensus algorithm is called \emph{proof-of-work}.
Where miners (parties that runs the Bitcoin network) collect transactions and compete in solving (using brute force) a difficult puzzle.
The first miner to solve it generates a block containing all the collected transactions.
The miner is also rewarded with new coins and transaction fees.
It is important to note that every block, that is the solution of the puzzle,
depends on the previous block.
Hence the name blockchain.
Further, due to the difficulty of the puzzle and that the majority of the parties are honest,
it is unlikely for more than one blockchain to exist in the network for a long period of time.
Thus every party sees a consistent blockchain which solves the double spending problem.
% Further, due to the reward mechanism,
% people are incentivised to act as miners and keep the system running.

Bitcoin has had its ups and downs, but over it has grown into an enormous system.
Its power consumption is as high as Republic of Ireland~\cite{o2014bitcoin}.
Its market cap, at the time of writing, is over 40 billion USD~\cite{bitcoinmarketcap}.
Many online marketplaces are using Bitcoin, for example Steam\footnote{\url{https://store.steampowered.com/}} and even Amazon\footnote{Not directly, but via \url{https://purse.io/}.}.
Due to its success, people from many different disciplines began investigating in way to use blockchain technology.
This includes finance~\cite{finance}, heathcare~\cite{healthcare}, logistics~\cite{supplychain} and energy~\cite{energy}.

Sadly, as traditional blockchain systems began to gain popularity,
their limitations also became apparent.
Bitcoin has the infamous 7 transactions per second upper bound~\cite{vukolic2015quest}.
This is due to the fact that blocks are fixed to 1 MB are only generated on average every 10 minutes.
Since every Bitcoin transaction is at least 250 bytes, it computes to about 7 transactions per second.
Due to this limitation, it is not uncommon to see a long backlog of about 20,000 transactions\footnote{\url{https://blockchain.info/unconfirmed-transactions/}}.
A few months ago the backlog even reached 100,000, which meant new transactions would take at least 11 hours to hit the blockchain~\cite{bitcoinbacklog}.
This issue has plagued the Bitcoin community for some time and is the root cause for the block size debate, which some calls it a civil war~\cite{bitcoincivilwar}.
Parties that are for the increase in block size argue that a larger block would improve the transaction rate.
Parties against it argue that it would make mining more centralised because blocks take longer to propogate through the network.
It also requires a hard fork (not backward compatible), which risks consensus failure and devaluation.
A recent empirical study by Croman et el.~\cite{croman2016scaling} has shown that increasing the block size may help.
But given the bandwidth and latency constraints,
it not possible to have more than 758 transactions per second.
Even worse, it may give some miner an unfair lead over others.
Thus fundamental changes are necessary run at the scale of centralised payment processors such as Visa~\cite{visa},
which is in the order of tens of thousands transactions per second.

What we have described is in fact the current state of Bitcoin.
Many proposals exist with the aim to make Bitcoin more scalable.
The most prominant is Seggregated Witness or SegWit~\cite{segwit}.
It moves the signature data to the end of the block and changes the block size to 4 MB.
The effect is that the first 1 MB of the block is still backward compatible, thus there is no need for a hard fork.
It also solves the transaction malleability problem~\cite{bitcoinmalleability} and paves the way for offchain transactions via Lightning Network~\cite{lightningnetwork}.
Although SegWit is implemented, it is still uncertain whether the Bitcoin network will adopt it.
At the time of writing, there is only 35\% of the network signalling for adoptation,
this is only a 10\% increase since November last year\footnote{\url{https://blockchain.info/charts/bip-9-segwit}}.
Thus it may take years if ever for SegWit to be adopted.
Even if it is adopted, it cannot reach the transaction rate of centralised systems.

In this work, we take the advice of Croman et el.~\cite{croman2016scaling} and Marko~\cite{vukolic2015quest} and rethink the blockchain architecture.
Our primary insight came from observing the differences between how transactional systems work in the real world and how they work in blockchain systems like Bitcoin. 
Take a restaurant owner for example, most of the time the customer is honest and pays the bill.
There is no need for the customer or the restaurant owner to report the transaction to any central authority 
because both parties are happy with the transaction.
On the other hand, if the customer leaves without paying the bill,
then the restaurant owner would report the incident to some central authority, e.g. the police.
On the contrary, in blockchain systems, every transaction is effectively sent to the miners,
which can be seen as a collective authority.
This consequently lead to limited scalability because every transaction must be validated by the authority even when most of the transaction are legitimate.

Using the aforementioned insight,
we explore an alternative consensus model for blockchain systems where transactions themself do not reach consensus,
but nevertheless verifiable at a later stage by any node in the network.
Informally, out model works as follows.
Every node stores its own blockchain and every block is one transaction.
We randomly selected nodes in every round, the selected ones are called facilitators.
They reach consensus not on the individual transactions,
but on the state of every chain represented by a single digest, we call this state the checkpoint.
If a checkpoint of some node is in consensus, 
then that node can proof to any other node that it holds a set of transactions that computes (form a chain) to the checkpoint.
This immediately show that those transactions are tamper-proof.

>>>>

We live in a world where technologies have become vital for our welfare and success.
The internet, for instance, gave us the ability of efficiently exchange information on a global scale.
However, in contrast to its original design, the internet and in particular the world wide web is becoming increasingly centralised.
The domain name system (root name server), certificate authorities (root CA), to name a few, carry enormous responsibilities and are a central point of failure.
The  same can be said for many other services such are online marketplaces,
cloud services, hospitality services and even our banking system.
The 2008 financial crisis is an example of the banking system making poor choices which resulted in a
decline in consumer wealth in the order of trillions~\cite{financialcrisis} and led to the European debt crisis.

Ironically, also in 2008, Satoshi Nakamoto published the Bitcoin whitepaper~\cite{bitcoin}.
Which, for the first time, gave us a simple banking system in the form of a distributed ledger, also known as blockchain.
It needs no central control but still incorruptable with high probability even if there are malicious parties that aim to undermine the system.

The primary innovations are (1) its consensus model which prevents double spending,
and (2) its incentive mechanism that encourages anyone (with adaquate hardware) to participate in the network and keep it running.
The double spending problem can be seen as an inconsistency issue.
For example, $C$ has 5 units of currency in her account.
If $C$ can simultaneously claim that she transferred 5 units to $A$ but also 5 units to $B$, then the system is inconsistent.
Bitcoin and many of its derivatives (e.g. Litecoin\footnote{\url{https://litecoin.org}} and Dogecoin\footnote{\url{http://dogecoin.org}}) solve the inconsistency problem with a consensus algorithm.
The goal of the algorithm is to reach agreement on a set of valid transactions. 
This effectively eliminates inconsistencies.

In Bitcoin's case, the consensus algorithm is called \emph{proof-of-work}.
Where miners (parties that runs the Bitcoin network) collect transactions and compete in solving a puzzle.
The puzzle is easy to verify but difficult to solve.
Only the miner that solves it can generate a valid block containing all the collected transactions.
The miner is also rewarded with new coins and transaction fees.
It is important to note that every block, that is the solution of the puzzle,
depends on the previous block.
Hence the name blockchain.
This property ensures malicious nodes cannot easily rewrite history if they do not have a majority of the network's computing power.
Consequently, it is unlikely for more than one blockchain to exist in the network for a long period of time.
Thus every party sees a consistent blockchain which solves the double spending problem.
% Further, due to the reward mechanism,
% people are incentivised to act as miners and keep the system running.

Bitcoin has had its ups and downs, but over it has grown into an enormous system.
Its power consumption is as high as Republic of Ireland~\cite{o2014bitcoin}.
Its market cap, at the time of writing, is over 40 billion USD~\cite{bitcoinmarketcap}.
% TODO add graph
Many online marketplaces are using Bitcoin, for example Steam\footnote{\url{https://store.steampowered.com/}} and even Amazon\footnote{Not directly, but via \url{https://purse.io/}.}.
Due to its success, people from many different disciplines began investigating in way to use blockchain technology.
This includes finance~\cite{finance}, heathcare~\cite{healthcare}, logistics~\cite{supplychain} and energy~\cite{energy}.

Sadly, as traditional blockchain systems began to gain popularity,
their limitations also became apparent.
Bitcoin has the infamous 7 transactions per second upper bound~\cite{vukolic2015quest}.
This is due to the fact that blocks are fixed to 1 MB are only generated on average every 10 minutes.
Since every Bitcoin transaction is at least 250 bytes, it computes to about 7 transactions per second.
Due to this limitation, it is not uncommon to see a long backlog of about 20,000 transactions\footnote{\url{https://blockchain.info/unconfirmed-transactions/}}.
A few months ago the backlog even reached 100,000, which meant new transactions would take at least 11 hours to be written to the blockchain~\cite{bitcoinbacklog}.
% TODO update below
This issue has plagued the Bitcoin community for some time and is the root cause for the block size debate, which some calls it a civil war~\cite{bitcoincivilwar}.
Parties that are for the increase in block size argue that a larger block would improve the transaction rate.
Parties against it argue that it would make mining more centralised because blocks take longer to propogate through the network.
It also requires a hard fork (not backward compatible), which risks consensus failure and devaluation.
% TODO update the above
A recent empirical study by Croman et el.~\cite{croman2016scaling} has shown that increasing the block size may help.
But given the bandwidth and latency constraints,
it is not possible to have more than 758 transactions per second.
Even worse, it may give some miner an unfair lead over others.
Thus fundamental changes are necessary run at the scale of centralised payment processors such as Visa,
which is in the order of tens of thousands transactions per second~\cite{visa}.

% TODO update
What we have described is in fact the current state of Bitcoin.
Many proposals exist with the aim to make Bitcoin more scalable.
The most prominant is Seggregated Witness or SegWit~\cite{segwit}.
It moves the signature data to the end of the block and changes the block size to 4 MB.
The effect is that the first 1 MB of the block is still backward compatible, thus there is no need for a hard fork.
It also solves the transaction malleability problem~\cite{bitcoinmalleability} and paves the way for offchain transactions via Lightning Network~\cite{lightningnetwork}.
Although SegWit is implemented, it is still uncertain whether the Bitcoin network will adopt it.
At the time of writing, there is only 35\% of the network signalling for adoptation,
this is only a 10\% increase since November last year\footnote{\url{https://blockchain.info/charts/bip-9-segwit}}.
Thus it may take years if ever for SegWit to be adopted.
Even if it is adopted, it cannot reach the transaction rate of centralised systems.
% https://www.bloomberg.com/news/articles/2017-07-10/bitcoin-risks-splintering-as-civil-war-enters-critical-month

In this work, we take the advice of Croman et el.~\cite{croman2016scaling} and Marko~\cite{vukolic2015quest} and rethink the blockchain architecture.
Our primary insight came from observing the differences between how transactional systems work in the real world and how they work in blockchain systems like Bitcoin. 
Take a restaurant owner for example, most of the time the customer is honest and pays the bill.
There is no need for the customer or the restaurant owner to report the transaction to any central authority 
because both parties are happy with the transaction.
On the other hand, if the customer leaves without paying the bill,
then the restaurant owner would report the incident to some central authority, e.g. the police.
On the contrary, in blockchain systems, every transaction is effectively sent to the miners,
which can be seen as a collective authority.
This consequently lead to limited scalability because every transaction must be validated by the authority even when most of the transactions are legitimate.

Using the aforementioned insight,
we explore an alternative consensus model for blockchain systems where transactions themself do not reach consensus,
but nevertheless verifiable at a later stage by any node in the network.
Informally, our system works as follows.
Every node stores its own blockchain and every block is one transaction.
We randomly select nodes in every round, the selected ones are called facilitators.
They reach consensus not on the individual transactions,
but on the state of every chain represented by a single digest, we call this state the checkpoint.
If a checkpoint of some node is in consensus, 
then that node can proof to any other node that it holds a set of transactions that computes (form a chain) to the checkpoint.
This immediately show that those transactions are tamper-proof.
% TODO mention consensus and trade off?

### 2017-07-29 thesis/chapters/ch2-problem.tex
Write more design variations
Edit ch1 and ch2

\chapter{Problem Description}
\label{ch:problem}

The decentralised and democratic nature of blockchain technology removes central point of control or failure.
However, as we described in the Introduction, it faces a genuine scalability problem.
In particular, proof-of-work based systems are unlikely to reach the transaction rate of Visa even with parameter tuning.
What we wish to see is horizontal scalability.
That is, by adding new nodes into the network, the global transaction rate should increase proportionally.
Hence, the research question we answer in this  work is the following.
\begin{displayquote}
\emph{How do we design a blockchain fabric that is fault tolerant, scalable and can reach global consensus?}
\end{displayquote}

In order to make sense of our research question, we must first define \emph{blockchain fabric}.
Typical blockchain systems are application specific.
For example, the application in Bitcoin (any many of its derivatives) is digital cash, the application in Namecoin is domain name registration~\cite{namecoin} and the application in Siacoin is cloud storage~\cite{siacoin}.
Underneath these applications lies the blockchain fabric which has the goal of reaching consensus on transactions.
In the case of Bitcoin it is proof-of-work (PoW).
It is not concerned with the structure of the transactions,
it works by simply treating transactions as a blob of data and hashes them with the previous block.
Hence, we focus on blockchain fabric rather than any specific application.
Because it is the scalability bottleneck and is neccessary for any blockchain based application.
% Also, it should be possible to build any kind of application on top our system.
% We do not impose on a consensus algorithm, as long as it satisfies the properties of atomic broadcast which we describe in~\Cref{sec:overview-cons}.

In the remainder of this chapter we expand on our research question and visit each of our requirement in detail.

\section{Global Consensus}

@@

Early blockchain systems use PoW as the consensus algorithm,
but consensus algorithm and especially Byzantine\footnote{Byzantine means participants can experience arbitrary failure, more on this in~\Cref{sec:acs-background}.}
consensus algorithms have existece since the 80s~\cite{pease1980reaching, lamport1982byzantine}.
The Practical Byzantine Fault Tolerance (PBFT) algorithm introduced in 1999 by Castro and Liskov~\cite{castro1999practical} is widely regarded as the first high-performance consensus algorithm.
The authors show that running PBFT in Network File System (NFS) was only 3\% slower than the standard unreplicated NFS.
Since then, research in this area picked up pace and many more algorithms are introduced~\cite{abd2005fault, kotla2007zyzzyva}.
With the introduction of Bitcoin's probabilistic consensus model, the field experienced a second renaissance.
These include proof-of-stake protocols~\cite{bentov2016snow, micali2016algorand}, as well as protocols optimised for blockchain~\cite{liu2016xft, miller2016honey}.

@@

\section{Security and Fault Tolerance}

@@

\section{Performance and Scalability}

@@

Traditional blockchain systems may run in a network of thousands of nodes, but the performance do not scale.
On the other hand, as we will see in~\Cref{sec:acs-background}, Byzantine consensus algorithms performs well but only when in a small network.
In this work we combine the ideas from both of these systems to create the first horizontally scalable blockchain fabric.

\section{Limitations}
Our work aims to significantly lower the transaction bound.
However, the price to pay is that the Sybil attack~\cite{douceur2002sybil} prevention mechanism moves from the blockchain fabric to the application layer.
For example, social network based Sybil defence mechanims use graph structure of real-world relationships~\cite{yu2006sybilguard}.
Online marketplaces such as Amazon use the rating of buyer and sellers.
Since our system is application neutral, we do not provide an explicit Sybil defence mechanism.
On the other hand, our system also has no restrictions on the Sybil defence technique
and applications built on top of our system can use the best mechanism for their purpose.

>>>>

\chapter{Problem description}
\label{ch:problem}

The decentralised and democratic nature of blockchain technology removes central point of control or failure.
However, as we described in the Introduction, it faces a genuine scalability problem.
In particular, proof-of-work based systems are unlikely to reach a transaction rate suitable for ubiquitous use, even with parameter tuning.
What we wish to see is horizontal scalability.
That is, by adding new nodes into the network, the global transaction rate should increase proportionally.
Hence, the research question we answer in this  work is the following.
\begin{displayquote}
\emph{How do we design a blockchain consensus protocol that is fault tolerant, scalable and can reach global consensus?}
\end{displayquote}

In order to make sense of our research question, we must first define \emph{blockchain consensus protocol}.
Typical blockchain systems are application specific.
For example, the application in Bitcoin (any many of its derivatives) is digital cash, the application in Namecoin is domain name registration~\cite{namecoin} and the application in Siacoin is cloud storage~\cite{siacoin}.
Underneath these applications lies the blockchain consensus protocol which has the goal of reaching consensus on transactions or state changes.
In the case of Bitcoin it is proof-of-work (PoW).
It is not concerned with the structure of the transactions,
it works by simply treating transactions as a blob of data and hashes them with the previous block.
In this work, we focus on the blockchain consensus protocol rather than any specific application.
Because it is the scalability bottleneck and is neccessary for any blockchain based application.
% Also, it should be possible to build any kind of application on top our system.
% We do not impose on a consensus algorithm, as long as it satisfies the properties of atomic broadcast which we describe in~\Cref{sec:overview-cons}.

In the remainder of this chapter we expand on our research question and visit each of our requirement in detail.
At the end of this chapter we describe some issues that we do not consider as a part of our design,
which is the result of not focusing on any specific application.

\section{Global consensus}

@@

Early blockchain systems use PoW as the consensus algorithm,
but consensus algorithm and especially Byzantine\footnote{Byzantine means participants can experience arbitrary failure, more on this in~\Cref{sec:acs-background}.}
consensus algorithms have existece since the 80s~\cite{pease1980reaching, lamport1982byzantine}.
The Practical Byzantine Fault Tolerance (PBFT) algorithm introduced in 1999 by Castro and Liskov~\cite{castro1999practical} is widely regarded as the first high-performance consensus algorithm.
The authors show that running PBFT in Network File System (NFS) was only 3\% slower than the standard unreplicated NFS.
Since then, research in this area picked up pace and many more algorithms are introduced, for example Q/U~\cite{abd2005fault} and Zyzzyva~\cite{kotla2007zyzzyva}.
With the introduction of Bitcoin's probabilistic consensus model, the field experienced a second renaissance.
These include proof-of-stake protocols~\cite{bentov2016snow, micali2016algorand}, as well as protocols optimised for blockchain~\cite{liu2016xft, miller2016honey}.

@@

\section{Security and fault tolerance}

@@

\section{Performance and scalability}

@@

Early blockchain systems may run in a network of thousands of nodes, but the performance do not scale.
On the other hand, as we will see in~\Cref{sec:acs-background}, Byzantine consensus algorithms performs well but only when in a small network.
In this work, our goal is to overcome the limitations of early blockchain systems and Byzantine consensus algorithms to create a horizontally scalable blockchain.

\section{Limitations}
Our work aims to significantly lower the transaction bound.
However, the price to pay is that the Sybil attack~\cite{douceur2002sybil} prevention mechanism moves from the blockchain consensus protocol to the application layer.
For example, social network based Sybil defence mechanims use graph structure of real-world relationships~\cite{yu2006sybilguard}.
Online marketplaces such as Amazon use the rating of buyer and sellers.
Since our system is application neutral, we do not provide an explicit Sybil defence mechanism.
On the other hand, our system also has no restrictions on the Sybil defence technique
and applications built on top of our system can use the best mechanism for their purpose.

For the same reason, we do not explicitly consider spam or denial of service attacks.
Without a concrete application it is difficult to distinguish a super active user from an attacker.
